% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res} 
% the margin option causes section titles to appear to the left of body text 
\textwidth=5.2in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage{hyperref}
\usepackage{enumitem}

\begin{document} 
\name{Zhiyan Foo\\[12pt]} % the \\[12pt] adds a blank line after name
 \setlist{nosep,after=}
\address{
    {\bf Email:} \href{mailto:zhiyanfoo@gmail.com}{\tt zhiyanfoo@gmail.com} \\
    {\bf Website:} \href{https://zhiyanfoo.github.io/}{\tt
    https://zhiyanfoo.github.io/} \\
    {\bf Github:} \href{https://github.com/zhiyanfoo}{\tt
    https://github.com/zhiyanfoo} \\
    {\bf Phone:} +65 84354397 
}

\address{ {\bf Address}\\
  Kang Ching Rd Blk 333 \\
    \# 08-264 \\
  Singapore, 610333
        }
 
\begin{resume} 
 
\section{Objective} 
A position in backend development or data analysis. 

\section{Background}
During high school and while in the army, I pursued my interest in programming
    by taking online courses as well as working on my own software projects. I've
    also studied mathematics intensely while in the army.

\section{Education} 
    {\bf Beijing BISS International School} -- Beijing, China.
\begin{itemize}
    \item International Baccalaureate (41/45 points).
    \item Higher Level Subjects: Math 6/7, Physics 7/7, Chemistry 7/7.
    \item Math Extended Essay (A).
\end{itemize}


\section{Employment}
    {\bf Army} -- Singapore Armed Forces, 02/2015 to 02/2017. (National Service)
 

\section{Technology}
    (good level) python, numpy; (basic level) Mathematica, C, Java, HTML, CSS,
    \LaTeX; (learning) Haskell.


\section{Projects}
    {\bf crunch-shake} -- A python library that evaluates scripts on
        the Bechdel Test and other similar metrics.
            Source Code : \href{https://github.com/zhiyanfoo/crunch-shake/}{\tt
            https://github.com/zhiyanfoo/crunch-shake/}.

\section{Additional Relevant Coursework} 

    {\bf Learning From Data} -- {\it Caltech telecourse}.
    \begin{itemize} \itemsep -2pt
        \item Introductory Machine Learning course focused on mathematical
            rigor. Machine learning
            algorithms like Percepton with Stochastic Gradient Descent,
            hard-margin Support Vector Machines and Logistic Regression built
            from scratch.
        \item Source Code :
    \href{https://github.com/zhiyanfoo/caltech-machine-learning/}{\tt
    https://github.com/zhiyanfoo/caltech-machine-learning/}
    \end{itemize} 
    {\bf Real Analysis, Convexity and Optimization} -- {\it Harvard Extension
    School}.
    \begin{itemize} \itemsep -2pt
        \item Upper-division pure math course focused on optimization problems
            with convex sets, normed infinite-dimensional vector spaces, and
            convex functionals.
    \end{itemize}
    {\bf AP Computer Science A} -- {\it American Advancement Placement Exam}. 
    \begin{itemize} \itemsep -2pt
            \item Score (5/5). Main topics included were sorting algorithms and
                object-oriented programming.
    \end{itemize}
    {\bf Algorithms on Strings} -- {\it Coursera, University of San Diego}. 
    \begin{itemize} \itemsep -2pt
        \item String compression and search algorithms  e.g. Suffix
            Trees, Burrows-Wheeler Transform and Knuth-Morris-Pratt.
    \end{itemize}
Complete list of coursework done can be found at
\href{https://zhiyanfoo.github.io/learning/}{\tt
https://zhiyanfoo.github.io/learning/}.
\section{Mathematics}
Linear Algebra, Multivariable Calculus, Differential Equations,
        Stochastic Systems, Real Analysis.

\end{resume} 
\end{document} 



