%-------------------------
% Resume in Latex
% Original Author : Sourabh Bajaj
% Modified By : Zhiyan Foo
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemAlt}[1]{
  \item\small{
    \textbf{#1}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\courseSubheading}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\courseItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[label={}]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Zhiyan Foo}} &
  zhiyanfoo@gmail.com\\
  \href{https://github.com/zhiyanfoo/}{github.com/zhiyanfoo} & +1 519 781
  2160 \\
\end{tabular*}

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \courseItem
     {\textsc{Languages -- } Python, Typescript, Golang, Haskell, Rust}
   \courseItem
     {\textsc{Tech/Frameworks -- } Kubernetes, Docker, *Nix, React/Redux, SQL}
 \resumeSubHeadingListEnd
%-------------------------------------

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Setter}{Rust, Typescript}
      {Full-Stack Developer Intern}{Jan 2019 - April 2019}
          \begin{itemize}[label={\textbullet}]
              \item Rewrote critical parts of the Node backend in Rust, e.g. transactional email
                  handling, realtime quote editor and service payment endpoints.
              \item Helped implement CI/CD (Travis, Docker) for microservices and investigate
                  moving from GCP to AWS.
          \end{itemize}

    \resumeSubheading
      {Got It}{Python}
      {Software Engineering Intern}{May 2018 - August 2018}
          \begin{itemize}[label={\textbullet}]
              \item Worked on the companies routing algorithms, the most
                  technically involved part of the companies stack. Extended the
                  system so we could perform real-time matching between professionals for
                  mentoring.
              \item Created API's and real-time channels for the first
                  mobile app used by our professionals. In particular wrote the backend service
                  to showcase real-time demand and analytics to our pro's.
          \end{itemize}
    \resumeSubheading
      {Quantcast}{Python}
      {Software Engineering Intern}{March 2017 - July 2017}
      \begin{itemize}[label={\textbullet}]
        \item Optimized performance of a real-time bidding configuration ETL (Extract, Transform,
            Load) pipeline. Cut down CPU time by \(\sim\) 30\%.
          \begin{itemize}
          \item Abstracted complex business logic as a graph and then
            implemented efficient graph traversal algorithms to perform the
            original business logic.
          \item Used indirection to reduce memory usage and number of sorts
            needed to shard domains.
          \end{itemize}
      \end{itemize}
  \resumeSubHeadingListEnd
%--------------------------------------

%------ADDITIONAL-COURSEWORK----------
\section{Additional Coursework}
 \resumeSubHeadingListStart
    \courseSubheading
      {Real Analysis, Convexity and Optimization}{Harvard Extension School}
      \resumeItemListStart
        \courseItem
          {Upper-division pure math course focused on optimization problems
            with convex sets, normed infinite-dimensional vector spaces, and
            convex functionals.}
      \resumeItemListEnd
    \courseSubheading
      {Learning From Data}{Caltech Telecourse}
      \resumeItemListStart
        \courseItem {Machine Learning Course:
    \href{https://github.com/zhiyanfoo/caltech-machine-learning/}{\tt
    github.com/zhiyanfoo/caltech-machine-learning/}}
      \resumeItemListEnd
\vspace{5pt}
\emph{I've been taking online college courses in addition to school or work since I was 16.
 It's how I started programming.} Complete list of additional coursework done can be found at
\href{https://zhiyanfoo.github.io/learning/}{\tt zhiyanfoo.github.io/learning/}. 
 \resumeSubHeadingListEnd
%-------------------------------------

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Zen}
      {An alternative to python's virtualenvwrapper that I personally use. 
            \href{https://github.com/zhiyanfoo/zen}{\tt
            https://github.com/zhiyanfoo/zen}
      }
\vspace*{0.2cm}
    \resumeSubItem{Chat App}
      {Chat service with Haskell backend (Websockets, Hspec) and Typescript
      frontend (React/Redux, Redux Saga).\\ 
\vspace*{0.2cm}
        \hskip 5.77em
            Source Code : \href{https://github.com/zhiyanfoo/chat-haskell-backend}{\tt
            https://github.com/zhiyanfoo/chat-haskell-backend}
            
        \hskip 5.77em
        Demo : 
\href{http://dadistcoder.com.s3-website-us-east-1.amazonaws.com/}{\tt
            http://dadistcoder.com.s3-website-us-east-1.amazonaws.com/}
            }
  \resumeSubHeadingListEnd
%-------------------------------------

%--------Fun--------------------------
\section{Extracurriculars}
 \resumeSubHeadingListStart
   \item{
       Haskell Club Founder. Soccer. Basketball. Dungeons and Dragons.
   }

 \resumeSubHeadingListEnd
%-------------------------------------------

%%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Waterloo}{Waterloo, CA}
      {Candidate for Bachelors of Mathematics (Pure Math)}{August 2017 -- Present}
  \resumeSubHeadingListEnd
%%-------------------------------------


\end{document}
